---
title: "DIS Spring 2026"
author: "AFN"
date: "2026-04-15"
output: 
  word_document: 
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages and Data 

```{r packages}
library(factoextra)
library(haven) #read .sav files
library(dplyr) #data cleaning and manipulation
library(tidyverse) #data cleaning and manipulation
library(sjlabelled) #get variable labels 
library(psych) #descriptive statistics
library(FactoMineR) #MCA function
library(paletteer) #color palette 'MoMAColors::Klein'
library(caret) #training and testing sets 
library(Metrics) #evaluate model metrics 
library(rsm)
```

```{r load data}
study2 <- read_sav('Data/Study2.sav')
# add relationship length variable 
study2 <- study2 %>%
  mutate(rel_length = case_when(
    # if relationship is less than one year, divid number of months by 12 for porportion of year
    length_months_1 >=1 ~ length_months_1/12,
    # if relationship is longer than one year, keep variable the same 
    length_years_1 >= 1 ~ length_years_1))

# create new dataframe with variables for analysis 
study2_clean <- study2 %>%
  select(
    p_age, #participant age
    p_gender, #participant gender
    p_SES, #MacArthur subjective social status scale 
    p_trans, #transgender identity (y/n)
    p_race, #particpant race 
    p_sexual_orientation, #participant sexual orientation
    rel_distance, #relationship long distance (y/n)
    rel_length, #relationship length in years 
    SWLS_1:SWLS_5, #satisfaction with life scale
    SMS_profiles, #number of individual social media profiles across all platforms
    SMS_visibility_1:SMS_visibility_5, #relationship visibility on social media
    IMS_daily_1:IMS_daily_6, #investment model scale satisfaction and commitment
    pos_neg_affect_1:pos_neg_affect_6, #positive and negative affect scale
    est_connect_1:est_connect_9, #self esteem scale 
    SMSdaily_active_1, #active social media use 
    SMSdaily_active_2,#passive social media use 
    rel_understanding_1:rel_understanding_5, #relative understanding by relationship partner
    SMS_plat_freq_1:SMS_plat_freq_10 #frequency of use of social media sites 
  )

# calculate social media frequency composite score based on the frequency 
# of use across all 10 platforms in the survey 
study2_clean <- study2_clean %>%
  mutate(SMS_freq_avg = rowMeans(pick(SMS_plat_freq_1:SMS_plat_freq_10), na.rm = TRUE))

# factor demographic variables 
study2_clean <- study2_clean %>%
  mutate(
    p_gender = factor(p_gender, labels = c('Agender',
                                           'Man',
                                           'Woman',
                                           'Non-binary')),
    p_trans = factor(p_trans, labels = c('Transgender',
                                         'Cisgender')),
    p_sexual_orientation = factor(p_sexual_orientation, labels = c('Asexual',
                                                                   'Bisexual',
                                                                   'Heterosexual',
                                                                   'Lesbian or Gay',
                                                                   'Pansexual',
                                                                   'Not listed')),
    rel_distance = factor(rel_distance, labels = c('Long distance',
                                                   'No long distance'))
  )
```

# MCA Analysis 

```{r mca dataset}
# create composite scores from scales 
study2_clean <- study2_clean %>%
  mutate(
    # satisfaction with life scale 
    SWLS_avg = rowMeans(pick(SWLS_1:SWLS_5), na.rm = TRUE),
    # online relationship visibility
    SMS_visibility_4R = 8 - SMS_visibility_4,
    SMS_visibility_avg = rowMeans(pick(SMS_visibility_1:SMS_visibility_3, SMS_visibility_4R, SMS_visibility_5), na.rm = TRUE),
    # investment model scale satisfaction
    IMS_sat = rowMeans(pick(IMS_daily_1:IMS_daily_3), na.rm = TRUE),
    # investment model commitment scale 
    IMS_com = rowMeans(pick(IMS_daily_4:IMS_daily_5), na.rm = TRUE),
    # total investment model scale 
    IMS_total = rowMeans(pick(IMS_daily_1:IMS_daily_6), na.rm = TRUE),
    # positive affect total 
    positive_affect = rowMeans(pick(pos_neg_affect_1:pos_neg_affect_3), na.rm = TRUE),
    # negative affect total 
    negative_affect = rowMeans(pick(pos_neg_affect_4:pos_neg_affect_6), na.rm = TRUE),
    # self esteem
    est_connect_1R = 8 - est_connect_1,
    est_connect_4R = 8 - est_connect_4,
    est_connect_5R = 8 - est_connect_5,
    est_connect_8R = 8 - est_connect_5, 
    esteem_avg = rowMeans(pick(est_connect_2, est_connect_3, est_connect_6, est_connect_7, est_connect_1R:est_connect_8R), na.rm = TRUE),
    rel_understanding_avg = rowMeans(pick(rel_understanding_1:rel_understanding_5), na.rm = TRUE)
  )

#bin continuous variables into categories 
study2_clean <- study2_clean %>%
  mutate(
    # satisfaction with life scale 
    SWLS_bin = cut(SWLS_avg, breaks = c(0, 2.33, 4.66, 7), labels = c('low','mid','high')),
    # online relationship visibility
    SMS_visibility_bin = cut(SMS_visibility_avg, breaks = c(0, 2.33, 4.66, 7), labels = c('low','mid','high')),
    # IMS satisfaction 
    IMS_sat_bin = cut(IMS_sat, breaks = c(0, 3, 6, 9), labels = c('low','mid','high')),
    # IMS commitment
    IMS_com_bin = cut(IMS_sat, breaks = c(0, 3, 6, 9), labels = c('low','mid','high')),
    #IMS total 
    IMS_total_bin = cut(IMS_total, breaks = c(0, 3, 6, 9), labels = c('low','mid','high')),
    # positive affect 
    positive_affect_bin = cut(positive_affect, breaks = c(0, 2.33, 4.66, 7), labels = c('low','mid','high')),
    # negative affect
    negative_affect_bin = cut(negative_affect, breaks = c(0,2.33,4.66,7), labels = c('low','mid','high')),
    #self esteem 
    esteem_bin = cut(esteem_avg, breaks = c(0, 2.33, 4.66, 7), labels = c('low','mid','high')),
    #relationship understanding
    rel_understanding_bin = cut(rel_understanding_avg, breaks = c(0, 1.66, 3.33, 5), labels = c('low','mid','high'))
  )

#isolate variables of interest for MCA
mca_bin_pred <- study2_clean %>%
  select(
    p_gender, #participant gender
    p_trans, #participant trans identity (y/n)
    p_sexual_orientation, #participant sexual orientation
    rel_distance, #relationship long distance (y/n)
    SWLS_bin, #satisfaction with life average 
    SMS_visibility_bin, #online relationship visibility average
    IMS_total_bin, #investment model composite score
    positive_affect_bin, #positive affect/mood 
    negative_affect_bin, #negative affect/mood 
    esteem_bin, #self-esteem score 
    rel_understanding_bin, #relationship understanding average 
    SMS_freq_avg #SMS frequency variable
  ) %>%
  na.omit()
```

Assess the number of important dimensions with a Scree plot. 

```{r mca model}
mca_bin_model <- MCA(mca_bin_pred, 
                     quanti.sup = 12, #do not use SMS frequency to build dimensions
                     graph = FALSE)
fviz_screeplot(mca_bin_model, 
               barfill = '#7E1A2FFF',
               barcolor = 'black') +
  theme(text = element_text(family = 'serif'))
```

Based on the scree plot, 3 or 4 dimensions are appropriate to explain the variation in the data. 

## MCA important variables 

Using Biplots, we can assess which variables are of the highest importance for each dimension.

### Dimensions 1 and 2

```{r dim 1 and 2 variable importance, dpi=300}
fviz_mca_var(mca_bin_model, choice = 'var', axes = c(1,2),
             font.family = 'serif', col.var = '#FF4D6FFF', col.quanti.sup = '#579EA4FF')
```

Variables further from the origin are more important to the dimensions. 

The most important variables for dimensions 1 and 2 are: 
* Investment model scale - Relationship quality
* Relative understanding - Relationship quality 
* Positive affect - overall quality of life
* negative affect - overall quality of life
* Satisfaction with life - subjective well-being
* Self-esteem - overall quality of life 

Taken together, these dimensions appear to clump together participants based on their subjective quality of life measures such as relationship quality and well-being. Based on this, we expect participants who report feeling low subjective well-being to also report lower relationship quality. 

### Dimensions 3 and 4
```{r dim 3 and 4 variable importance, dpi=300}
fviz_mca_var(mca_bin_model, choice = 'var', axes = c(3,4),
             font.family = 'serif', col.var = '#FF4D6FFF', col.quanti.sup = '#579EA4FF')
```

The variables participant gender and participant sexual orientation are important to dimension 3 and 4. The variable relationship long distance is important to dimension 4 but not dimension 3. Participant transgender identity is important to dimension 3 but not 4. 

These dimensions are based on gender and sexual orientation. Based on these dimensions, we would expect to see categories of people based on their minority gender and sexuality status. 

## Individual Participants 

We can visualize each participant's score on dimensions based on the categories of our important variables. 

### Dimensions 1 and 2

```{r ind plot dims 1 and 2 IMS, dpi=300}
fviz_mca_ind(mca_bin_model,
             label = 'none',
             habillage = 'IMS_total_bin',
             addEllipses = TRUE, ellipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2)) +
  scale_color_paletteer_d('MoMAColors::Klein')
```

```{r relative understanding, dpi=300}
fviz_mca_ind(mca_bin_model,
             label = 'none',
             habillage = 'rel_understanding_bin',
             addEllipses = TRUE, ellipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2)) +
  scale_color_paletteer_d('MoMAColors::Klein')
```