---
title: "DIS Spring 2026"
author: "Amy_Neal"
date: "2026-04-21"
output: 
  powerpoint_presentation: 
    fig_width: 15
    fig_height: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r source model script, include=FALSE}
source('presentation_script.R', local = knitr::knit_global())
```

```{r packages, warning=FALSE, message=FALSE}
library(cowplot)
library(flextable)
```
# Introduction

## About the Data 
```{r}
flextable(describe(study2_clean$esteem_avg))
```

# MCA Analysis

## Scree Plot of Dimensions 
```{r, dpi=600}
fviz_screeplot(mca_model.3,
               barfill = '#7E1A2FFF',
               barcolor = 'black') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 28),
        axis.title = element_text(size = 30)) +
  labs(title = '')
```

## Important Variables Dimensions 1 and 2
```{r, dpi=600}
fviz_mca_var(mca_model.3, choice = 'var', axes = c(1,2),
             font.family = 'serif', col.var = '#FF4D6FFF', col.quanti.sup = '#579EA4FF',
             repel = TRUE,
             labelsize = 12,
             pointsize = 5) +
  theme(axis.text = element_text(size = 28),
        axis.title = element_text(size = 30),
        plot.margin = unit(c(0,0,0,0), 'cm')) +
  labs(title = '')
```

## Variable Importance Dimension 1
```{r, dpi=600}
fviz_contrib(mca_model.3, 
             choice = 'var', 
             top = 20, 
             axes = c(1), 
             fill = '#2D2651FF',
             color = 'black') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 30),
        plot.margin = unit(c(0,0,0,3), 'cm')) +
  labs(title = '')
```

## Variable Importance Dimension 2
```{r, dpi=600}
fviz_contrib(mca_model.3, 
             choice = 'var', 
             top = 20, 
             axes = c(2), 
             fill = '#2D2651FF',
             color = 'black') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 30),
        plot.margin = unit(c(0,0,0,2), 'cm')) +
  labs(title = '')
```

## Relationship Qulaity Dimensions 1 and 2
```{r}
fviz_mca_ind(mca_model.3,
             label = 'none',
             habillage = 'IMS_total_bin',
             addEllipses = TRUE, ellipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2),
             pointsize = 2.5) +
  scale_color_paletteer_d('MoMAColors::Klein') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 26),
        plot.title = element_text(size = 30),
        legend.position = 'none') +
  labs(title = 'Relationship Quality')
```

## Relationship Quality Dimensions 3 and 4
```{r}
fviz_mca_ind(mca_model.3,
             label = 'none',
             habillage = 'IMS_total_bin',
             addEllipses = TRUE, ellipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(3,4),
             pointsize = 2.5) +
  scale_color_paletteer_d('MoMAColors::Klein') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 26),
        plot.title = element_text(size = 30),
        legend.position = 'none') +
  labs(title = 'Relationship Quality')
```

## Important Variables for Dimensions 3 and 4
```{r}
fviz_mca_var(mca_model.3, choice = 'var', axes = c(3,4),
             font.family = 'serif', col.var = '#FF4D6FFF', col.quanti.sup = '#579EA4FF',
             repel = TRUE,
             labelsize = 12,
             pointsize = 5) +
  theme(axis.text = element_text(size = 28),
        axis.title = element_text(size = 30),
        plot.margin = unit(c(0,0,0,0), 'cm')) +
  labs(title = '')
```

## Variable Importance Dimension 3 
```{r, dpi=600}
fviz_contrib(mca_model.3, 
             choice = 'var', 
             top = 20, 
             axes = c(3), 
             fill = '#2D2651FF',
             color = 'black') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 30)) +
  labs(title = '')
```

## Variable Importance Dimension 4
```{r, dpi=600}
fviz_contrib(mca_model.3, 
             choice = 'var', 
             top = 20, 
             axes = c(4), 
             fill = '#2D2651FF',
             color = 'black') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 30)) +
  labs(title = '')
```

## Individuals on Dimensions 3 and 4
```{r}
fviz_mca_ind(mca_model.3,
             label = 'none',
             habillage = 'p_trans',
             addEllipses = TRUE, ellipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(3,4),
             pointsize = 2.5) +
  scale_color_paletteer_d('MoMAColors::Klein') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 26),
        plot.title = element_text(size = 30),
        legend.position = 'none') +
  labs(title = 'Transgender Identity')
```

## Gender and Dimensions 3 and 4 
```{r}
fviz_mca_ind(mca_model.3,
             label = 'none',
             habillage = 'p_gender',
             addEllipses = TRUE, ellipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(3,4),
             pointsize = 2.5) +
  scale_color_paletteer_d('MoMAColors::Klein') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 26),
        plot.title = element_text(size = 30),
        legend.position = 'none') +
  labs(title = 'Participant Gender')
```

## Relationship long distance and dimensions 3 and 4 
```{r}
fviz_mca_ind(mca_model.3,
             label = 'none',
             habillage = 'rel_distance',
             addEllipses = TRUE, ellipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(3,4),
             pointsize = 2.5) +
  scale_color_paletteer_d('MoMAColors::Klein') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 26),
        plot.title = element_text(size = 30),
        legend.position = 'none') +
  labs(title = 'Relationship Long-Distance')
```

## Sexual orientation and dimensions 3 and 4 
```{r}
fviz_mca_ind(mca_model.3,
             label = 'none',
             habillage = 'p_sexual_orientation',
             addEllipses = TRUE, ellipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(3,4),
             pointsize = 2.5) +
  scale_color_paletteer_d('MoMAColors::Klein') +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 26),
        plot.title = element_text(size = 30),
        legend.position = 'none') +
  labs(title = 'Sexual Orientation')
```

# Generalized Linear Model

## Model 

$Y_i = -1.51D_1 + 0.26D_2 - 0.24D_3 - 0.35D_4$

## Likelihood Ratio of Deviance 
```{r}
pchisq(q = glm.model.4$null.deviance - glm.model.4$deviance,
       df = glm.model.4$df.null - glm.model.4$df.residual, 
       lower.tail = FALSE)
```

# Supplementary Slides 

## Self-esteem by Relationship Quality 
```{r, dpi=300}
ggplot(data = mca_pred_esteem,
       aes(x = esteem_avg)) +
  geom_density(aes(fill = IMS_total_bin), alpha = .7) +
  geom_vline(aes(xintercept = mean(esteem_avg)), linetype = 'dashed') +
  theme_classic() +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 28),
        legend.title = element_text(size = 28),
        legend.text = element_text(size = 24)) +
  labs(x = 'Self-Esteem') +
  scale_fill_paletteer_d('MoMAColors::Klein', name = 'Relationship Quality', label = c('Low','Ambivalent','High'))
```

## Self-esteem by Relative Understanding 
```{r}
ggplot(data = mca_pred_esteem,
       aes(x = esteem_avg)) +
  geom_density(aes(fill = rel_understanding_bin), alpha = .7) +
  geom_vline(aes(xintercept = mean(esteem_avg)), linetype = 'dashed') +
  theme_classic() +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 28),
        legend.title = element_text(size = 28),
        legend.text = element_text(size = 24)) +
  labs(x = 'Self-Esteem') +
  scale_fill_paletteer_d('MoMAColors::Klein', 
                         name = 'Understanding', 
                         label = c('Low','Ambivalent','High'))
```

## Self-esteem by SWLS
```{r}
ggplot(data = mca_pred_esteem,
       aes(x = esteem_avg)) +
  geom_density(aes(fill = SWLS_bin), alpha = .7) +
  geom_vline(aes(xintercept = mean(esteem_avg)), linetype = 'dashed') +
  theme_classic() +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 28),
        legend.title = element_text(size = 28),
        legend.text = element_text(size = 24)) +
  labs(x = 'Self-Esteem') +
  scale_fill_paletteer_d('MoMAColors::Klein', 
                         name = 'Well-Being', 
                         label = c('Low','Middle','High'))
```

## Self-esteem by Gender 
```{r}
ggplot(data = mca_pred_esteem,
       aes(x = esteem_avg)) +
  geom_density(aes(fill = p_gender), alpha = .7) +
  geom_vline(aes(xintercept = mean(esteem_avg)), linetype = 'dashed') +
  theme_classic() +
  theme(text = element_text(family = 'serif'),
        axis.text = element_text(size = 24),
        axis.title = element_text(size = 28),
        legend.title = element_text(size = 28),
        legend.text = element_text(size = 24)) +
  labs(x = 'Self-Esteem') +
  scale_fill_paletteer_d('MoMAColors::Klein', 
                         name = 'Understanding') 
```
