---
title: "Study 3 Analyses"
author: "AFN"
date: "2026-06-16"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
source('Study3_analyses.R', local = knitr::knit_global())
```

# Exploratory Data Analyses 

## Participant Gender 

```{r}
table(study3_mca$p_gender)
```

```{r}
plot(study3_mca$p_gender)
```

## Participant Age

```{r}
describe(study3_mca$p_age)
```

```{r}
hist(study3_mca$p_age)
```

```{r}
boxplot(study3_mca$p_age)
```

## Participant Sexual Orientation

```{r}
table(study3_mca$p_sexual_orientation)
```

```{r}
plot(study3_mca$p_sexual_orientation)
```

## Participant Socioeconomic Status 

```{r}
table(study3_mca$p_SES)
```

```{r}
hist(study3_mca$p_SES)
```

## Investment Model Scale Averages

```{r}
describe(select(study3_mca, IMS_sat_avg, IMS_com_avg, IMS_alt_avg, IMS_inv_avg))
```

```{r}
hist(study3_mca$IMS_sat_avg)
```

```{r}
hist(study3_mca$IMS_com_avg)
```

```{r}
hist(study3_mca$IMS_alt_avg)
```

```{r}
hist(study3_mca$IMS_inv_avg)
```

## Self-esteem

```{r}
describe(study3_mca$SelfEsteem_avg)
```

```{r}
hist(study3_mca$SelfEsteem_avg)
```

## Satisfaction with Life 

```{r}
describe(study3_mca$SWLS_avg)
```

```{r}
hist(study3_mca$SWLS_avg)
```

```{r}
boxplot(study3$SWLS_avg)
```

## Active and Passive Social Media Use 

```{r}
describe(select(study3_mca, SMS_active_passive_1, SMS_active_passive_2))
```

```{r}
hist(study3_mca$SMS_active_passive_1)
```

```{r}
hist(study3_mca$SMS_active_passive_2)
```

## Online Relationship Visibility

```{r}
describe(study3_mca$relation_visibility)
```

```{r}
hist(study3_mca$relation_visibility)
```

# MCA Analysis 

```{r}
fviz_screeplot(s3_mca)
```

```{r}
summary(s3_mca, nbelements = Inf)
```

## Dimension 1

```{r}
fviz_contrib(s3_mca, choice = 'var', top = 20, axes = 1)
```

## Dimension 2

```{r}
fviz_contrib(s3_mca, choice = 'var', top = 20, axes = 2)
```

## Dimensions 1 and 2

Important variables on both dimensions 

```{r}
fviz_mca_ind(s3_mca, 
             label = 'none',
             habillage = 'IMS_sat_bin',
             addEllipses = TRUE, elipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2))
```

Relationship Satisfaction 

```{r}
fviz_mca_ind(s3_mca, 
             label = 'none',
             habillage = 'IMS_sat_bin',
             addEllipses = TRUE, elipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2))
```

Relationship Commitment

```{r}
fviz_mca_ind(s3_mca, 
             label = 'none',
             habillage = 'IMS_com_bin',
             addEllipses = TRUE, elipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2))
```

Quality of Alternatives 

```{r}
fviz_mca_ind(s3_mca, 
             label = 'none',
             habillage = 'IMS_alt_bin',
             addEllipses = TRUE, elipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2))
```

Relationship Investment 

```{r}
fviz_mca_ind(s3_mca, 
             label = 'none',
             habillage = 'IMS_inv_bin',
             addEllipses = TRUE, elipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2))
```

Satisfaction with Life 

```{r}
fviz_mca_ind(s3_mca, 
             label = 'none',
             habillage = 'SWLS_bin',
             addEllipses = TRUE, elipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(1,2))
```

## Dimension 3

```{r}
fviz_contrib(s3_mca, choice = 'var', top = 20, axes = 3)
```

## Dimension 4

```{r}
fviz_contrib(s3_mca, choice = 'var', top = 20, axes = 4)
```

## Dimensions 3 and 4

Variable importance for both dimensions 

```{r}
fviz_mca_var(s3_mca, choice = 'var', axes = c(3,4))
```

Active social media use 

```{r}
fviz_mca_ind(s3_mca, 
             label = 'none',
             habillage = 'SMS_active_passive_1',
             addEllipses = TRUE, elipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(3,4))
```

Passive social media use 

```{r}
fviz_mca_ind(s3_mca, 
             label = 'none',
             habillage = 'SMS_active_passive_2',
             addEllipses = TRUE, elipse.type = 'confidence',
             ggtheme = theme_minimal(),
             axes = c(3,4))
```


